---
dataMaid: yes
title: Codebook for Human Activity Table (data)
date: 2020-08-30 09:39:22
output: html_document
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```

```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```

# Data report overview
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations      10299

Number of variables            69
---------------------------------




# Codebook summary table

----------------------------------------------------------------------------------
Label   Variable                      Class       # unique  Missing  Description  
                                                    values                        
------- ----------------------------- --------- ---------- --------- -------------
        **[test]**                    factor             2  0.00 %                

        **[activity]**                factor             6  0.00 %                

        **[subject]**                 factor            30  0.00 %                

        **[Time                       numeric        10292  0.00 %                
        BodyAcc-mean-X]**                                                         

        **[Time                       numeric        10299  0.00 %                
        BodyAcc-mean-Y]**                                                         

        **[Time                       numeric        10293  0.00 %                
        BodyAcc-mean-Z]**                                                         

        **[Time                       numeric        10296  0.00 %                
        GravityAcc-mean-X]**                                                      

        **[Time                       numeric        10298  0.00 %                
        GravityAcc-mean-Y]**                                                      

        **[Time                       numeric        10299  0.00 %                
        GravityAcc-mean-Z]**                                                      

        **[Time                       numeric        10299  0.00 %                
        BodyAccJerk-mean-X]**                                                     

        **[Time                       numeric        10299  0.00 %                
        BodyAccJerk-mean-Y]**                                                     

        **[Time                       numeric        10299  0.00 %                
        BodyAccJerk-mean-Z]**                                                     

        **[Time                       numeric        10298  0.00 %                
        BodyGyro-mean-X]**                                                        

        **[Time                       numeric        10299  0.00 %                
        BodyGyro-mean-Y]**                                                        

        **[Time                       numeric        10297  0.00 %                
        BodyGyro-mean-Z]**                                                        

        **[Time                       numeric        10295  0.00 %                
        BodyGyroJerk-mean-X]**                                                    

        **[Time                       numeric        10299  0.00 %                
        BodyGyroJerk-mean-Y]**                                                    

        **[Time                       numeric        10298  0.00 %                
        BodyGyroJerk-mean-Z]**                                                    

        **[Time                       numeric        10296  0.00 %                
        BodyAccMag-mean]**                                                        

        **[Time                       numeric        10296  0.00 %                
        GravityAccMag-mean]**                                                     

        **[Time                       numeric        10292  0.00 %                
        BodyAccJerkMag-mean]**                                                    

        **[Time                       numeric        10298  0.00 %                
        BodyGyroMag-mean]**                                                       

        **[Time                       numeric        10293  0.00 %                
        BodyGyroJerkMag-mean]**                                                   

        **[FFT                        numeric        10295  0.00 %                
        BodyAcc-mean-X]**                                                         

        **[FFT                        numeric        10292  0.00 %                
        BodyAcc-mean-Y]**                                                         

        **[FFT                        numeric        10295  0.00 %                
        BodyAcc-mean-Z]**                                                         

        **[FFT                        numeric        10293  0.00 %                
        BodyAccJerk-mean-X]**                                                     

        **[FFT                        numeric        10296  0.00 %                
        BodyAccJerk-mean-Y]**                                                     

        **[FFT                        numeric        10294  0.00 %                
        BodyAccJerk-mean-Z]**                                                     

        **[FFT                        numeric        10297  0.00 %                
        BodyGyro-mean-X]**                                                        

        **[FFT                        numeric        10296  0.00 %                
        BodyGyro-mean-Y]**                                                        

        **[FFT                        numeric        10297  0.00 %                
        BodyGyro-mean-Z]**                                                        

        **[FFT                        numeric        10296  0.00 %                
        BodyAccMag-mean]**                                                        

        **[FFT                        numeric        10290  0.00 %                
        BodyBodyAccJerkMag-mean]**                                                

        **[FFT                        numeric        10297  0.00 %                
        BodyBodyGyroMag-mean]**                                                   

        **[FFT                        numeric        10293  0.00 %                
        BodyBodyGyroJerkMag-mean]**                                               

        **[Time                       numeric        10295  0.00 %                
        BodyAcc-std-X]**                                                          

        **[Time                       numeric        10297  0.00 %                
        BodyAcc-std-Y]**                                                          

        **[Time                       numeric        10297  0.00 %                
        BodyAcc-std-Z]**                                                          

        **[Time                       numeric        10288  0.00 %                
        GravityAcc-std-X]**                                                       

        **[Time                       numeric        10293  0.00 %                
        GravityAcc-std-Y]**                                                       

        **[Time                       numeric        10296  0.00 %                
        GravityAcc-std-Z]**                                                       

        **[Time                       numeric        10290  0.00 %                
        BodyAccJerk-std-X]**                                                      

        **[Time                       numeric        10296  0.00 %                
        BodyAccJerk-std-Y]**                                                      

        **[Time                       numeric        10293  0.00 %                
        BodyAccJerk-std-Z]**                                                      

        **[Time                       numeric        10292  0.00 %                
        BodyGyro-std-X]**                                                         

        **[Time                       numeric        10296  0.00 %                
        BodyGyro-std-Y]**                                                         

        **[Time                       numeric        10296  0.00 %                
        BodyGyro-std-Z]**                                                         

        **[Time                       numeric        10292  0.00 %                
        BodyGyroJerk-std-X]**                                                     

        **[Time                       numeric        10295  0.00 %                
        BodyGyroJerk-std-Y]**                                                     

        **[Time                       numeric        10291  0.00 %                
        BodyGyroJerk-std-Z]**                                                     

        **[Time                       numeric        10294  0.00 %                
        BodyAccMag-std]**                                                         

        **[Time                       numeric        10294  0.00 %                
        GravityAccMag-std]**                                                      

        **[Time                       numeric        10294  0.00 %                
        BodyAccJerkMag-std]**                                                     

        **[Time                       numeric        10298  0.00 %                
        BodyGyroMag-std]**                                                        

        **[Time                       numeric        10297  0.00 %                
        BodyGyroJerkMag-std]**                                                    

        **[FFT                        numeric        10294  0.00 %                
        BodyAcc-std-X]**                                                          

        **[FFT                        numeric        10297  0.00 %                
        BodyAcc-std-Y]**                                                          

        **[FFT                        numeric        10296  0.00 %                
        BodyAcc-std-Z]**                                                          

        **[FFT                        numeric        10291  0.00 %                
        BodyAccJerk-std-X]**                                                      

        **[FFT                        numeric        10294  0.00 %                
        BodyAccJerk-std-Y]**                                                      

        **[FFT                        numeric        10290  0.00 %                
        BodyAccJerk-std-Z]**                                                      

        **[FFT                        numeric        10297  0.00 %                
        BodyGyro-std-X]**                                                         

        **[FFT                        numeric        10293  0.00 %                
        BodyGyro-std-Y]**                                                         

        **[FFT                        numeric        10295  0.00 %                
        BodyGyro-std-Z]**                                                         

        **[FFT                        numeric        10298  0.00 %                
        BodyAccMag-std]**                                                         

        **[FFT                        numeric        10296  0.00 %                
        BodyBodyAccJerkMag-std]**                                                 

        **[FFT                        numeric        10296  0.00 %                
        BodyBodyGyroMag-std]**                                                    

        **[FFT                        numeric        10292  0.00 %                
        BodyBodyGyroJerkMag-std]**                                                
----------------------------------------------------------------------------------




# Variable list
## test

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                        "train"

Reference category             test
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-1-test', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("test", 
"train"), class = "factor"), y = c(2947L, 7352L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "test")
```

</div>
</div>


- Observed factor levels: \"test\", \"train\". 



---

## activity

<div class = "row">
<div class = "col-lg-8">

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                 factor

Number of missing obs.       0 (0 %)

Number of unique values            6

Mode                        "LAYING"

Reference category            LAYING
------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-2-activity', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, .Label = c("LAYING", 
"SITTING", "STANDING", "WALKING", "WALKING_DOWNSTAIRS", "WALKING_UPSTAIRS"
), class = "factor"), y = c(1944L, 1777L, 1906L, 1722L, 1406L, 
1544L)), class = "data.frame", row.names = c(NA, -6L)), vnam = "activity")
```

</div>
</div>


- Observed factor levels: \"LAYING\", \"SITTING\", \"STANDING\", \"WALKING\", \"WALKING_DOWNSTAIRS\", \"WALKING_UPSTAIRS\". 



---

## subject

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values          30

Mode                           "25"

Reference category                1
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-3-subject', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:30, .Label = c("1", 
"2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", 
"14", "15", "16", "17", "18", "19", "20", "21", "22", "23", "24", 
"25", "26", "27", "28", "29", "30"), class = "factor"), y = c(347L, 
302L, 341L, 317L, 302L, 325L, 308L, 281L, 288L, 294L, 316L, 320L, 
327L, 323L, 328L, 366L, 368L, 364L, 360L, 354L, 408L, 321L, 372L, 
381L, 409L, 392L, 376L, 382L, 344L, 383L)), class = "data.frame", row.names = c(NA, 
-30L)), vnam = "subject")
```

</div>
</div>


- Observed factor levels: \"1\", \"10\", \"11\", \"12\", \"13\", \"14\", \"15\", \"16\", \"17\", \"18\", \"19\", \"2\", \"20\", \"21\", \"22\", \"23\", \"24\", \"25\", \"26\", \"27\", \"28\", \"29\", \"3\", \"30\", \"4\", \"5\", \"6\", \"7\", \"8\", \"9\". 



---

## Time BodyAcc-mean-X

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values          10292

Median                            0.28

1st and 3rd quartiles       0.26; 0.29

Min. and max.                    -1; 1
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-4-Time-BodyAcc-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 0L, 0L, 3L, 7L, 4L, 5L, 8L, 
17L, 72L, 643L, 7579L, 1679L, 257L, 14L, 7L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "Time BodyAcc-mean-X")
```

</div>
</div>




---

## Time BodyAcc-mean-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10299

Median                             -0.02

1st and 3rd quartiles       -0.02; -0.01

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-5-Time-BodyAcc-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 0L, 0L, 3L, 3L, 3L, 2L, 4L, 90L, 
8855L, 1283L, 30L, 15L, 5L, 1L, 2L, 1L, 0L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "Time BodyAcc-mean-Y")
```

</div>
</div>




---

## Time BodyAcc-mean-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10293

Median                            -0.11

1st and 3rd quartiles       -0.12; -0.1

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-6-Time-BodyAcc-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 1L, 1L, 0L, 8L, 9L, 29L, 218L, 7132L, 
2742L, 111L, 25L, 8L, 7L, 1L, 1L, 0L, 1L, 1L, 2L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "Time BodyAcc-mean-Z")
```

</div>
</div>




---

## Time GravityAcc-mean-X

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values          10296

Median                            0.92

1st and 3rd quartiles       0.81; 0.95

Min. and max.                    -1; 1
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-7-Time-GravityAcc-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(24L, 24L, 82L, 83L, 247L, 392L, 322L, 
413L, 273L, 80L, 2L, 16L, 1L, 24L, 17L, 17L, 151L, 319L, 1650L, 
6162L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time GravityAcc-mean-X")
```

</div>
</div>




---

## Time GravityAcc-mean-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10298

Median                            -0.14

1st and 3rd quartiles       -0.24; 0.12

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-8-Time-GravityAcc-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(27L, 0L, 0L, 0L, 35L, 301L, 1141L, 2311L, 
2075L, 1078L, 659L, 367L, 273L, 192L, 274L, 306L, 205L, 354L, 
309L, 392L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time GravityAcc-mean-Y")
```

</div>
</div>




---

## Time GravityAcc-mean-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10299

Median                             0.04

1st and 3rd quartiles       -0.12; 0.22

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-9-Time-GravityAcc-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(52L, 1L, 0L, 2L, 51L, 213L, 500L, 801L, 
1180L, 1551L, 2077L, 1210L, 614L, 409L, 254L, 205L, 364L, 191L, 
387L, 237L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time GravityAcc-mean-Z")
```

</div>
</div>




---

## Time BodyAccJerk-mean-X

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values          10299

Median                            0.08

1st and 3rd quartiles       0.06; 0.09

Min. and max.                    -1; 1
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-10-Time-BodyAccJerk-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 12L, 16L, 46L, 78L, 169L, 280L, 
435L, 691L, 6179L, 959L, 591L, 336L, 242L, 127L, 62L, 44L, 23L, 
6L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccJerk-mean-X")
```

</div>
</div>




---

## Time BodyAccJerk-mean-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10299

Median                             0.01

1st and 3rd quartiles       -0.02; 0.03

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-11-Time-BodyAccJerk-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4L, 5L, 13L, 15L, 60L, 111L, 232L, 411L, 
670L, 1767L, 5405L, 699L, 433L, 233L, 119L, 67L, 36L, 9L, 7L, 
3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccJerk-mean-Y")
```

</div>
</div>




---

## Time BodyAccJerk-mean-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10299

Median                                0

1st and 3rd quartiles       -0.03; 0.02

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-12-Time-BodyAccJerk-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(3L, 9L, 8L, 18L, 51L, 120L, 222L, 440L, 
727L, 3775L, 3509L, 662L, 357L, 214L, 101L, 43L, 22L, 11L, 6L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccJerk-mean-Z")
```

</div>
</div>




---

## Time BodyGyro-mean-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10298

Median                             -0.03

1st and 3rd quartiles       -0.05; -0.01

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-13-Time-BodyGyro-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 6L, 19L, 78L, 138L, 254L, 305L, 
312L, 536L, 6405L, 1013L, 363L, 255L, 304L, 212L, 74L, 18L, 4L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyro-mean-X")
```

</div>
</div>




---

## Time BodyGyro-mean-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10299

Median                            -0.07

1st and 3rd quartiles       -0.1; -0.05

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-14-Time-BodyGyro-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 1L, 8L, 21L, 58L, 132L, 286L, 568L, 
1640L, 5994L, 820L, 394L, 214L, 89L, 44L, 15L, 9L, 3L, 0L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyro-mean-Y")
```

</div>
</div>




---

## Time BodyGyro-mean-Z

<div class = "row">
<div class = "col-lg-8">

--------------------------------------
Feature                         Result
------------------------- ------------
Variable type                  numeric

Number of missing obs.         0 (0 %)

Number of unique values          10297

Median                            0.09

1st and 3rd quartiles       0.06; 0.11

Min. and max.                    -1; 1
--------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-15-Time-BodyGyro-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(2L, 5L, 6L, 7L, 26L, 42L, 79L, 125L, 
227L, 614L, 6051L, 2154L, 457L, 230L, 126L, 64L, 46L, 26L, 6L, 
6L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyro-mean-Z")
```

</div>
</div>




---

## Time BodyGyroJerk-mean-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10295

Median                              -0.1

1st and 3rd quartiles       -0.12; -0.08

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-16-Time-BodyGyroJerk-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(3L, 1L, 10L, 17L, 57L, 151L, 310L, 736L, 
2950L, 4684L, 744L, 388L, 150L, 52L, 25L, 12L, 7L, 0L, 1L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerk-mean-X")
```

</div>
</div>




---

## Time BodyGyroJerk-mean-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10299

Median                             -0.04

1st and 3rd quartiles       -0.06; -0.03

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-17-Time-BodyGyroJerk-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 2L, 3L, 14L, 25L, 42L, 170L, 431L, 
997L, 6770L, 1088L, 458L, 172L, 74L, 32L, 10L, 6L, 2L, 1L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerk-mean-Y")
```

</div>
</div>




---

## Time BodyGyroJerk-mean-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10298

Median                             -0.05

1st and 3rd quartiles       -0.08; -0.03

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-18-Time-BodyGyroJerk-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(1L, 6L, 6L, 13L, 40L, 98L, 223L, 540L, 
1158L, 6277L, 1104L, 485L, 195L, 90L, 35L, 18L, 4L, 2L, 3L, 1L
)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerk-mean-Z")
```

</div>
</div>




---

## Time BodyAccMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.87

1st and 3rd quartiles       -0.98; -0.12

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-19-Time-BodyAccMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5016L, 356L, 110L, 51L, 27L, 84L, 347L, 
893L, 1058L, 821L, 551L, 477L, 286L, 144L, 41L, 11L, 7L, 13L, 
3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccMag-mean")
```

</div>
</div>




---

## Time GravityAccMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.87

1st and 3rd quartiles       -0.98; -0.12

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-20-Time-GravityAccMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5016L, 356L, 110L, 51L, 27L, 84L, 347L, 
893L, 1058L, 821L, 551L, 477L, 286L, 144L, 41L, 11L, 7L, 13L, 
3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time GravityAccMag-mean")
```

</div>
</div>




---

## Time BodyAccJerkMag-mean

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10292

Median                            -0.95

1st and 3rd quartiles       -0.99; -0.3

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-21-Time-BodyAccJerkMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5508L, 107L, 42L, 109L, 328L, 711L, 
872L, 844L, 755L, 531L, 249L, 124L, 58L, 32L, 10L, 10L, 3L, 3L, 
1L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccJerkMag-mean")
```

</div>
</div>




---

## Time BodyGyroMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10298

Median                             -0.82

1st and 3rd quartiles       -0.98; -0.25

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-22-Time-BodyGyroMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4702L, 534L, 199L, 132L, 193L, 623L, 
842L, 963L, 837L, 556L, 342L, 184L, 91L, 50L, 28L, 10L, 4L, 5L, 
2L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroMag-mean")
```

</div>
</div>




---

## Time BodyGyroJerkMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10293

Median                             -0.96

1st and 3rd quartiles       -0.99; -0.55

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-23-Time-BodyGyroJerkMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5528L, 129L, 450L, 1097L, 1038L, 903L, 
501L, 304L, 155L, 80L, 54L, 30L, 13L, 9L, 5L, 1L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerkMag-mean")
```

</div>
</div>




---

## FFT BodyAcc-mean-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10295

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.26

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-24-FFT-BodyAcc-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5422L, 136L, 39L, 83L, 202L, 639L, 908L, 
798L, 654L, 459L, 370L, 296L, 161L, 76L, 28L, 12L, 6L, 7L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAcc-mean-X")
```

</div>
</div>




---

## FFT BodyAcc-mean-Y

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10292

Median                            -0.86

1st and 3rd quartiles       -0.98; -0.1

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-25-FFT-BodyAcc-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4912L, 462L, 126L, 53L, 50L, 150L, 395L, 
755L, 849L, 758L, 619L, 478L, 311L, 172L, 96L, 48L, 37L, 15L, 
7L, 6L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAcc-mean-Y")
```

</div>
</div>




---

## FFT BodyAcc-mean-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10295

Median                              -0.9

1st and 3rd quartiles       -0.98; -0.37

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-26-FFT-BodyAcc-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5106L, 335L, 102L, 332L, 605L, 891L, 
1028L, 780L, 441L, 238L, 187L, 105L, 66L, 37L, 22L, 13L, 6L, 
2L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyAcc-mean-Z")
```

</div>
</div>




---

## FFT BodyAccJerk-mean-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10293

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.33

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-27-FFT-BodyAccJerk-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5526L, 88L, 43L, 189L, 448L, 777L, 888L, 
728L, 552L, 416L, 322L, 155L, 86L, 39L, 17L, 13L, 9L, 2L, 0L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAccJerk-mean-X")
```

</div>
</div>




---

## FFT BodyAccJerk-mean-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.93

1st and 3rd quartiles       -0.98; -0.26

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-28-FFT-BodyAccJerk-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5366L, 212L, 68L, 143L, 313L, 620L, 
727L, 790L, 731L, 519L, 363L, 234L, 91L, 63L, 37L, 11L, 7L, 3L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAccJerk-mean-Y")
```

</div>
</div>




---

## FFT BodyAccJerk-mean-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10294

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.51

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-29-FFT-BodyAccJerk-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5497L, 186L, 483L, 854L, 827L, 937L, 
626L, 358L, 229L, 112L, 77L, 56L, 23L, 13L, 12L, 4L, 2L, 2L, 
0L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAccJerk-mean-Z")
```

</div>
</div>




---

## FFT BodyGyro-mean-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.89

1st and 3rd quartiles       -0.99; -0.38

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-30-FFT-BodyGyro-mean-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5093L, 374L, 135L, 282L, 616L, 1060L, 
937L, 721L, 452L, 288L, 154L, 77L, 45L, 23L, 14L, 9L, 8L, 6L, 
2L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyGyro-mean-X")
```

</div>
</div>




---

## FFT BodyGyro-mean-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.92

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-31-FFT-BodyGyro-mean-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5303L, 244L, 206L, 792L, 968L, 780L, 
667L, 457L, 299L, 211L, 147L, 81L, 61L, 27L, 19L, 13L, 15L, 5L, 
1L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyGyro-mean-Y")
```

</div>
</div>




---

## FFT BodyGyro-mean-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.89

1st and 3rd quartiles       -0.99; -0.32

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-32-FFT-BodyGyro-mean-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5051L, 468L, 88L, 165L, 381L, 776L, 
1006L, 833L, 627L, 397L, 204L, 117L, 62L, 49L, 34L, 21L, 11L, 
3L, 4L, 2L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyGyro-mean-Z")
```

</div>
</div>




---

## FFT BodyAccMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.22

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-33-FFT-BodyAccMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5013L, 352L, 121L, 82L, 187L, 617L, 
790L, 696L, 647L, 550L, 376L, 318L, 250L, 129L, 90L, 39L, 20L, 
11L, 6L, 5L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyAccMag-mean")
```

</div>
</div>




---

## FFT BodyBodyAccJerkMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10290

Median                             -0.93

1st and 3rd quartiles       -0.99; -0.26

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-34-FFT-BodyBodyAccJerkMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5362L, 212L, 66L, 109L, 304L, 603L, 
784L, 686L, 612L, 575L, 420L, 249L, 141L, 75L, 52L, 17L, 21L, 
5L, 3L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyBodyAccJerkMag-mean")
```

</div>
</div>




---

## FFT BodyBodyGyroMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.88

1st and 3rd quartiles       -0.98; -0.45

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-35-FFT-BodyBodyGyroMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4936L, 521L, 179L, 592L, 986L, 1043L, 
769L, 491L, 308L, 191L, 115L, 65L, 36L, 26L, 20L, 11L, 5L, 3L, 
1L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyBodyGyroMag-mean")
```

</div>
</div>




---

## FFT BodyBodyGyroJerkMag-mean

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10293

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.61

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-36-FFT-BodyBodyGyroJerkMag-mean', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5446L, 348L, 874L, 1191L, 971L, 567L, 
318L, 188L, 130L, 103L, 64L, 36L, 32L, 11L, 9L, 3L, 6L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyBodyGyroJerkMag-mean")
```

</div>
</div>




---

## Time BodyAcc-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10295

Median                             -0.94

1st and 3rd quartiles       -0.99; -0.25

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-37-Time-BodyAcc-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5407L, 141L, 40L, 64L, 106L, 537L, 970L, 
872L, 580L, 479L, 349L, 292L, 208L, 140L, 69L, 20L, 11L, 9L, 
4L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAcc-std-X")
```

</div>
</div>




---

## Time BodyAcc-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.84

1st and 3rd quartiles       -0.98; -0.06

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-38-Time-BodyAcc-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4774L, 482L, 162L, 87L, 44L, 60L, 208L, 
579L, 960L, 838L, 724L, 519L, 349L, 250L, 125L, 62L, 38L, 17L, 
12L, 9L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAcc-std-Y")
```

</div>
</div>




---

## Time BodyAcc-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.85

1st and 3rd quartiles       -0.98; -0.28

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-39-Time-BodyAcc-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4881L, 420L, 143L, 133L, 323L, 650L, 
965L, 963L, 624L, 422L, 288L, 213L, 116L, 60L, 37L, 21L, 18L, 
14L, 5L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time BodyAcc-std-Z")
```

</div>
</div>




---

## Time GravityAcc-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10288

Median                             -0.98

1st and 3rd quartiles       -0.99; -0.96

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-40-Time-GravityAcc-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9719L, 401L, 84L, 22L, 24L, 10L, 14L, 
6L, 5L, 1L, 1L, 1L, 3L, 2L, 1L, 2L, 1L, 1L, 0L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "Time GravityAcc-std-X")
```

</div>
</div>




---

## Time GravityAcc-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10293

Median                             -0.98

1st and 3rd quartiles       -0.99; -0.95

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-41-Time-GravityAcc-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(9334L, 692L, 127L, 65L, 20L, 6L, 17L, 
11L, 10L, 4L, 5L, 1L, 2L, 0L, 1L, 0L, 1L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "Time GravityAcc-std-Y")
```

</div>
</div>




---

## Time GravityAcc-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.97

1st and 3rd quartiles       -0.99; -0.93

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-42-Time-GravityAcc-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(8695L, 1101L, 261L, 108L, 42L, 30L, 
18L, 11L, 5L, 6L, 6L, 3L, 2L, 3L, 2L, 3L, 0L, 1L, 1L, 1L)), class = "data.frame", row.names = c(NA, 
-20L)), vnam = "Time GravityAcc-std-Z")
```

</div>
</div>




---

## Time BodyAccJerk-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10290

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.29

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-43-Time-BodyAccJerk-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5526L, 88L, 38L, 129L, 342L, 689L, 840L, 
744L, 592L, 501L, 351L, 249L, 102L, 53L, 23L, 15L, 10L, 5L, 0L, 
2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccJerk-std-X")
```

</div>
</div>




---

## Time BodyAccJerk-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.93

1st and 3rd quartiles       -0.99; -0.22

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-44-Time-BodyAccJerk-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5353L, 224L, 60L, 119L, 271L, 472L, 
685L, 696L, 698L, 647L, 424L, 281L, 176L, 90L, 53L, 33L, 8L, 
6L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time BodyAccJerk-std-Y")
```

</div>
</div>




---

## Time BodyAccJerk-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10293

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.55

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-45-Time-BodyAccJerk-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5524L, 220L, 632L, 933L, 917L, 849L, 
547L, 284L, 158L, 101L, 74L, 28L, 16L, 8L, 5L, 1L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyAccJerk-std-Z")
```

</div>
</div>




---

## Time BodyGyro-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10292

Median                              -0.9

1st and 3rd quartiles       -0.99; -0.48

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-46-Time-BodyGyro-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5156L, 328L, 263L, 711L, 1083L, 985L, 
737L, 460L, 281L, 162L, 65L, 34L, 12L, 6L, 9L, 5L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyro-std-X")
```

</div>
</div>




---

## Time BodyGyro-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.91

1st and 3rd quartiles       -0.98; -0.45

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-47-Time-BodyGyro-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5232L, 302L, 115L, 509L, 1052L, 882L, 
593L, 438L, 344L, 283L, 258L, 115L, 54L, 48L, 33L, 20L, 15L, 
1L, 2L, 3L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time BodyGyro-std-Y")
```

</div>
</div>




---

## Time BodyGyro-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.88

1st and 3rd quartiles       -0.99; -0.34

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-48-Time-BodyGyro-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5003L, 488L, 128L, 200L, 458L, 790L, 
1038L, 902L, 593L, 301L, 129L, 87L, 56L, 34L, 29L, 28L, 11L, 
11L, 7L, 6L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time BodyGyro-std-Z")
```

</div>
</div>




---

## Time BodyGyroJerk-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10292

Median                             -0.93

1st and 3rd quartiles       -0.99; -0.49

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-49-Time-BodyGyroJerk-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5391L, 206L, 309L, 738L, 955L, 994L, 
699L, 474L, 238L, 130L, 76L, 41L, 22L, 12L, 5L, 4L, 2L, 0L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerk-std-X")
```

</div>
</div>




---

## Time BodyGyroJerk-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10295

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.63

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-50-Time-BodyGyroJerk-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5522L, 554L, 934L, 967L, 834L, 557L, 
341L, 183L, 124L, 104L, 56L, 44L, 22L, 24L, 14L, 8L, 4L, 4L, 
1L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerk-std-Y")
```

</div>
</div>




---

## Time BodyGyroJerk-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10291

Median                             -0.95

1st and 3rd quartiles       -0.99; -0.51

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-51-Time-BodyGyroJerk-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5511L, 116L, 337L, 774L, 1088L, 924L, 
645L, 377L, 212L, 130L, 74L, 50L, 32L, 9L, 13L, 5L, 0L, 0L, 0L, 
2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerk-std-Z")
```

</div>
</div>




---

## Time BodyAccMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10294

Median                             -0.84

1st and 3rd quartiles       -0.98; -0.24

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-52-Time-BodyAccMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4865L, 407L, 143L, 81L, 276L, 648L, 
804L, 862L, 676L, 383L, 341L, 329L, 236L, 145L, 62L, 26L, 6L, 
5L, 3L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time BodyAccMag-std")
```

</div>
</div>




---

## Time GravityAccMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10294

Median                             -0.84

1st and 3rd quartiles       -0.98; -0.24

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-53-Time-GravityAccMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4865L, 407L, 143L, 81L, 276L, 648L, 
804L, 862L, 676L, 383L, 341L, 329L, 236L, 145L, 62L, 26L, 6L, 
5L, 3L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time GravityAccMag-std")
```

</div>
</div>




---

## Time BodyAccJerkMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10294

Median                             -0.93

1st and 3rd quartiles       -0.99; -0.27

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-54-Time-BodyAccJerkMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5349L, 223L, 73L, 105L, 359L, 699L, 
732L, 690L, 583L, 565L, 381L, 274L, 113L, 85L, 29L, 21L, 8L, 
7L, 2L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "Time BodyAccJerkMag-std")
```

</div>
</div>




---

## Time BodyGyroMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10298

Median                             -0.83

1st and 3rd quartiles       -0.98; -0.39

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-55-Time-BodyGyroMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4607L, 657L, 252L, 407L, 831L, 920L, 
801L, 670L, 460L, 286L, 155L, 103L, 62L, 31L, 27L, 19L, 4L, 3L, 
2L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroMag-std")
```

</div>
</div>




---

## Time BodyGyroJerkMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.94

1st and 3rd quartiles       -0.99; -0.61

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-56-Time-BodyGyroJerkMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5414L, 405L, 890L, 1126L, 943L, 618L, 
304L, 191L, 130L, 90L, 66L, 51L, 31L, 17L, 7L, 7L, 4L, 2L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "Time BodyGyroJerkMag-std")
```

</div>
</div>




---

## FFT BodyAcc-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10294

Median                             -0.94

1st and 3rd quartiles       -0.99; -0.25

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-57-FFT-BodyAcc-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5411L, 130L, 44L, 56L, 124L, 524L, 966L, 
805L, 623L, 459L, 369L, 247L, 213L, 156L, 82L, 55L, 19L, 8L, 
3L, 5L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAcc-std-X")
```

</div>
</div>




---

## FFT BodyAcc-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.83

1st and 3rd quartiles       -0.98; -0.09

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-58-FFT-BodyAcc-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4776L, 467L, 170L, 84L, 49L, 104L, 344L, 
737L, 916L, 882L, 656L, 441L, 289L, 191L, 93L, 51L, 24L, 13L, 
9L, 3L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAcc-std-Y")
```

</div>
</div>




---

## FFT BodyAcc-std-Z

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values           10296

Median                            -0.84

1st and 3rd quartiles       -0.98; -0.3

Min. and max.                     -1; 1
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-59-FFT-BodyAcc-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4842L, 425L, 163L, 167L, 360L, 782L, 
1000L, 848L, 539L, 372L, 304L, 236L, 118L, 44L, 30L, 16L, 24L, 
14L, 11L, 4L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyAcc-std-Z")
```

</div>
</div>




---

## FFT BodyAccJerk-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10291

Median                             -0.96

1st and 3rd quartiles       -0.99; -0.32

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-60-FFT-BodyAccJerk-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5543L, 79L, 44L, 176L, 435L, 755L, 857L, 
713L, 613L, 420L, 321L, 176L, 93L, 37L, 20L, 8L, 5L, 1L, 1L, 
2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAccJerk-std-X")
```

</div>
</div>




---

## FFT BodyAccJerk-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10294

Median                             -0.93

1st and 3rd quartiles       -0.99; -0.24

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-61-FFT-BodyAccJerk-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5370L, 220L, 58L, 144L, 297L, 502L, 
693L, 689L, 641L, 582L, 449L, 266L, 162L, 97L, 70L, 34L, 15L, 
6L, 2L, 2L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyAccJerk-std-Y")
```

</div>
</div>




---

## FFT BodyAccJerk-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10290

Median                             -0.96

1st and 3rd quartiles       -0.99; -0.59

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-62-FFT-BodyAccJerk-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5550L, 311L, 824L, 947L, 959L, 732L, 
459L, 222L, 121L, 84L, 55L, 19L, 10L, 4L, 0L, 0L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAccJerk-std-Z")
```

</div>
</div>




---

## FFT BodyGyro-std-X

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10297

Median                             -0.91

1st and 3rd quartiles       -0.99; -0.52

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-63-FFT-BodyGyro-std-X', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5191L, 320L, 385L, 979L, 1082L, 852L, 
608L, 413L, 233L, 125L, 61L, 24L, 10L, 7L, 6L, 1L, 0L, 0L, 1L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyGyro-std-X")
```

</div>
</div>




---

## FFT BodyGyro-std-Y

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10293

Median                             -0.91

1st and 3rd quartiles       -0.98; -0.44

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-64-FFT-BodyGyro-std-Y', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5202L, 328L, 119L, 457L, 1036L, 896L, 
624L, 386L, 347L, 245L, 208L, 192L, 102L, 66L, 27L, 25L, 12L, 
17L, 8L, 2L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyGyro-std-Y")
```

</div>
</div>




---

## FFT BodyGyro-std-Z

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10295

Median                             -0.89

1st and 3rd quartiles       -0.99; -0.42

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-65-FFT-BodyGyro-std-Z', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5080L, 439L, 179L, 390L, 727L, 1094L, 
945L, 668L, 340L, 156L, 102L, 59L, 32L, 27L, 19L, 18L, 10L, 6L, 
3L, 5L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyGyro-std-Z")
```

</div>
</div>




---

## FFT BodyAccMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10298

Median                             -0.85

1st and 3rd quartiles       -0.98; -0.38

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-66-FFT-BodyAccMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4916L, 388L, 130L, 322L, 703L, 1060L, 
944L, 546L, 401L, 381L, 277L, 158L, 53L, 11L, 4L, 2L, 1L, 0L, 
1L, 1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyAccMag-std")
```

</div>
</div>




---

## FFT BodyBodyAccJerkMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.93

1st and 3rd quartiles       -0.99; -0.31

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-67-FFT-BodyBodyAccJerkMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5334L, 231L, 97L, 160L, 507L, 781L, 
653L, 604L, 580L, 490L, 378L, 225L, 134L, 66L, 30L, 16L, 3L, 
6L, 3L, 1L)), class = "data.frame", row.names = c(NA, -20L)), 
    vnam = "FFT BodyBodyAccJerkMag-std")
```

</div>
</div>




---

## FFT BodyBodyGyroMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10296

Median                             -0.83

1st and 3rd quartiles       -0.98; -0.47

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-68-FFT-BodyBodyGyroMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(4638L, 634L, 400L, 755L, 1029L, 878L, 
736L, 541L, 289L, 160L, 84L, 73L, 30L, 18L, 21L, 9L, 2L, 0L, 
0L, 2L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyBodyGyroMag-std")
```

</div>
</div>




---

## FFT BodyBodyGyroJerkMag-std

<div class = "row">
<div class = "col-lg-8">

----------------------------------------
Feature                           Result
------------------------- --------------
Variable type                    numeric

Number of missing obs.           0 (0 %)

Number of unique values            10292

Median                             -0.94

1st and 3rd quartiles       -0.99; -0.64

Min. and max.                      -1; 1
----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-69-FFT-BodyBodyGyroJerkMag-std', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(-1, -0.9, -0.8, -0.7, 
-0.6, -0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 
0.6, 0.7, 0.8, 0.9), xmax = c(-0.9, -0.8, -0.7, -0.6, -0.5, -0.4, 
-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 
0.9, 1), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0), ymax = c(5414L, 579L, 1104L, 1100L, 791L, 510L, 
298L, 160L, 114L, 74L, 50L, 35L, 29L, 16L, 11L, 5L, 4L, 2L, 2L, 
1L)), class = "data.frame", row.names = c(NA, -20L)), vnam = "FFT BodyBodyGyroJerkMag-std")
```

</div>
</div>




---



Report generation information:

 *  Created by: Denis Levert (username: `DenisLevert`).

 *  Report creation time: Sun Aug 30 2020 09:39:23

 *  Report was run from directory: `/Users/DenisLevert/Documents/R/R_School/CleanData/Project/HumanActivity`

 *  dataMaid v1.4.0 [Pkg: 2019-12-10 from CRAN (R 4.0.2)]

 *  R version 4.0.2 (2020-06-22).

 *  Platform: x86_64-apple-darwin17.0 (64-bit)(macOS Catalina 10.15.6).

 *  Function call: `dataMaid::makeDataReport(data = data, mode = c("summarize", "visualize", 
"check"), smartNum = FALSE, file = "codebook_data.Rmd", checks = list(
    character = "showAllFactorLevels", factor = "showAllFactorLevels", 
    labelled = "showAllFactorLevels", haven_labelled = "showAllFactorLevels", 
    numeric = NULL, integer = NULL, logical = NULL, Date = NULL), 
    listChecks = FALSE, maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for data")`

